Resolvable Ambiguity

### 2019-07-11 paper/paper.tex
More work on 6.3

@@

\noindent We then combine them into a single visibly pushdown automaton. Every time we transition from a production to a child we push a symbol to the stack, which we then pop when we go back. We use $Q \times Q$ as our stack alphabet, to record the transition we are replacing in the parent. We thus replace every edge $p \xrightarrow{l_\top} q$, where $l \in \Labels$, with:

@@

\noindent Finally, we add a new initial state and a new final state, and connect them with the initial and final states belonging to the starting non-terminal:

@@

>>>>

\subsubsection{Example for Simplified Construction}

@@

\noindent We then combine the DFAs into a single visibly pushdown automaton. Every time we transition from a production to a child we push a symbol to the stack, which we then pop when we return. We use $Q \times Q$ as our stack alphabet, to record the transition we are replacing in the parent. We thus replace every edge $p \xrightarrow{l_\top} q$, where $l \in \Labels$, with:

@@

\noindent Finally, we add a new initial state and a new final state, and connect them to the initial and final states belonging to the starting non-terminal:

@@

\subsubsection{Example for Full Construction}
